\vspace{-2cm} Content of Municipal Government Websites

### 2017-03-29 paper/manuscript.tex
added less confusing table with snapshot dates

The use of asymmetric priors \citep{Wallach2009} in our topic model - i.e. the assumption that some topics, such as administrative content, are inherently more common - may be a more elegant way of dealing with this issue.

@@

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Sun Mar 26 22:39:59 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{rllllllllllllllll}
		\hline
		Date & Attica & Connersville & Frankfort & Huntingburg & Indianapolis & Lake Station & Linton & Madison & Mitchell & Monticello & North Vernon & Richmond & Rockport & South Bend & Union City & Winchester \\ 
		\hline
		20150701.00 & 20141219004329 & 20090608160638 & 20150801164305 & 20150326174031 & 20080705032706 & 20150801185836 & 20130907112731 & 20150623192440 & 20150801214647 & 20150701005605 & 20150801221031 & 20150702075332 & 20150617220801 & 20150627165751 & 20150925160622 & 20150925022240 \\ 
		20150801.00 & 20160129070621 & 20090608160638 & 20150801164305 & 20151030133234 & 20080705032706 & 20150801185836 & 20130907112731 & 20150801210044 & 20150801214647 & 20150804061315 & 20150801221031 & 20150802055917 & 20150801070026 & 20150726161609 & 20150925160622 & 20150925022240 \\ 
		20150901.00 & 20160129070621 & 20090608160638 & 20150918063903 & 20151030133234 & 20080705032706 & 20150906164302 & 20130907112731 & 20150901105012 & 20150811063416 & 20150905074509 & 20150829185257 & 20150904033112 & 20150909192825 & 20150905085030 & 20150925160622 & 20150925022240 \\ 
		20151001.00 & 20160129070621 & 20090608160638 & 20150925070028 & 20151030133234 & 20080705032706 & 20150908103757 & 20130907112731 & 20150905063305 & 20150811063416 & 20150908082732 & 20150829185257 & 20150921033423 & 20151011085644 & 20151002075030 & 20150925160622 & 20150925022240 \\ 
		20151101.00 & 20160129070621 & 20090608160638 & 20151113140944 & 20151030133234 & 20080705032706 & 20151029043137 & 20130907112731 & 20151110090517 & 20160111041751 & 20151110131337 & 20151103095602 & 20151031212522 & 20151021163057 & 20151101043016 & 20150925160622 & 20151026092123 \\ 
		20151201.00 & 20160129070621 & 20090608160638 & 20151121002259 & 20151030133234 & 20080705032706 & 20151201114611 & 20130907112731 & 20151216063136 & 20160111041751 & 20151115102706 & 20151206224620 & 20151201073504 & 20151212093554 & 20151209044311 & 20160111224058 & 20151127174603 \\ 
		20160101.00 & 20160129070621 & 20090608160638 & 20160110065704 & 20160113165318 & 20080705032706 & 20160101144553 & 20130907112731 & 20151228192543 & 20160111041751 & 20151228224908 & 20160111074656 & 20160102015111 & 20160110195124 & 20151229083812 & 20160111224058 & 20151127174603 \\ 
		20160201.00 & 20160129070621 & 20090608160638 & 20160127035634 & 20160122005059 & 20080705032706 & 20160201195326 & 20130907112731 & 20160201073437 & 20160202113637 & 20160206015204 & 20160111074656 & 20160213102047 & 20160112154213 & 20160206190816 & 20160111224058 & 20160303215247 \\ 
		20160301.00 & 20160330220432 & 20090608160638 & 20160304094239 & 20160221045049 & 20080705032706 & 20160303165533 & 20130907112731 & 20160303181704 & 20160301141845 & 20160304035215 & 20160309122910 & 20160302140643 & 20160112154213 & 20160303175057 & 20160111224058 & 20160303215247 \\ 
		20160401.00 & 20160330220432 & 20090608160638 & 20160321173048 & 20160317192932 & 20080705032706 & 20160404133508 & 20130907112731 & 20160402214824 & 20160405050341 & 20160403012946 & 20160318230947 & 20160403090645 & 20160603041333 & 20160325014215 & 20160111224058 & 20160416084956 \\ 
		20160501.00 & 20160330220432 & 20090608160638 & 20160424080036 & 20160317192932 & 20080705032706 & 20160507020142 & 20130907112731 & 20160504014532 & 20160507154306 & 20160511155648 & 20160420092957 & 20160502154350 & 20160603041333 & 20160427024310 & 20160111224058 & 20160422124026 \\ 
		20160601.00 & 20160330220432 & 20090608160638 & 20160424080036 & 20160317192932 & 20080705032706 & 20160507020142 & 20130907112731 & 20160521233726 & 20160507154306 & 20160522012629 & 20160420092957 & 20160522061744 & 20160603041333 & 20160522075620 & 20160111224058 & 20160517165930 \\ 
		\hline
	\end{tabular}
	\caption{Dates of WaybackMachine snapshots 2015-16} 
\end{table}

>>>>

The use of asymmetric priors \citep{Wallach2009} over the document topic distribution - i.e. the assumption that some topics, such as administrative content, are inherently more common - may be a more elegant way of dealing with this issue.

@@

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 29 11:30:05 2017
\begin{table}[ht]
	\centering
	\begin{tabular}{lllr}
		\hline
		City & snapshotPrior & electionDay & daysToElection \\ 
		\hline
		Attica & 2015-08-01 & 2015-11-03 & 94 \\ 
		Cornersville & 2015-10-18 & 2015-11-03 & 16 \\ 
		Frankfort & 2015-10-18 & 2015-11-03 & 16 \\ 
		Huntingburg & 2015-10-30 & 2015-11-03 & 4 \\ 
		Indianapolis & 2015-10-16 & 2015-11-03 & 18 \\ 
		Lake Station & 2015-10-29 & 2015-11-03 & 5 \\ 
		Linton & 2015-08-01 & 2015-11-03 & 94 \\ 
		Madison & 2015-09-05 & 2015-11-03 & 59 \\ 
		Mitchell &  & 2015-11-03 &  \\ 
		Monticello & 2015-09-08 & 2015-11-03 & 56 \\ 
		North Vernon & 2015-11-03 & 2015-11-03 & 0 \\ 
		Richmond & 2015-10-31 & 2015-11-03 & 3 \\ 
		Rockport & 2015-10-21 & 2015-11-03 & 13 \\ 
		South Bend & 2015-11-01 & 2015-11-03 & 2 \\ 
		Union City & 2015-09-25 & 2015-11-03 & 39 \\ 
		Winchester & 2015-10-26 & 2015-11-03 & 8 \\ 
		\hline
	\end{tabular}
	\caption{Closest snapshots to election day} 
\end{table}
